\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-04-22 paper/main.tex
Add 20% of drugs discussion todo to discussion

One major component of our experiments was to determine how the
information that is available to a machine learning model during
training affects the performance of the model. Similarly to previous
work \cite{MolTrans2020, DeepConvDTI2019}, we find significant
differences in predictive performance across different splitting
schemes.

>>>>

\todo[inline]{Why is having only having 20\% of drugs reasonable -> significance test in results}
One major component of our experiments was to determine how the
information that is available to a machine learning model during
training affects the performance of the model. Similarly to previous
work \cite{MolTrans2020, DeepConvDTI2019}, we find significant
differences in predictive performance across different splitting
schemes.
